---
title: "Exam 1"
format: html
---

```{r}
# install.packages("tidytuesdayR")
# install.packages("tidyverse")
# 
# library(tidytuesdayR)
# library(tidyverse)
# 
# tuesdata <- tt_load('2020-02-18')
# fc <- tuesdata$food_consumption
```

```{r}
# head(fc)
# dim(fc)
# str(fc)
```

```{r}
# # Country
# ggplot(fc, aes(x = country)) +
#   geom_bar()
# # Food item
# ggplot(fc, aes(x = food_category)) +
#   geom_bar()
# # Consumption
# ggplot(fc, aes(y = consumption)) +
#   geom_histogram()
```

Overall food consumption / food category
*This would be a simple bar graph*
Overall food consumption / country
*This would also be a simple bar graph*

For answering question 9, I would select a stacked bar chart.
  This chart would have axes labels, alt text, a caption, a legend, and a title.
  
Some further questions I have are
1. How does world region of affect consumption?
2. How does a country's size affect consumption?
3. How are CO2 emmissions related to food consumption?
4. How are CO2 emmissions related to food category?

